Proximal compact spaces are Corson compact

### 2014-04-22 articles/proximity-corson/proximity-corson.tex
first round of revisions

We quickly note a couple properites of $\frac{1}{2}D$.

\begin{prop}
  If $x\in \frac{1}{2}D[y]$ and $y\in \frac{1}{2}D[z]$, then $x\in D[z]$
\end{prop}

@@

The theory of proximal uniform spaces relies on the following $\omega$-length game:

\begin{defn}
  The \textbf{proximal game} $\proxgame{X}$ of length $\omega$ played on a uniform space $X$ with two players $\pl D$, $\pl P$ proceeds as follows:
    \begin{itemize}
      \item In the initial round $0$, $\pl D$ chooses an open symmetric entourage $D_0$, followed by $\pl P$ choosing a point $p_0\in X$.
      \item In round $n+1$, $\pl D$ chooses an open symmetric entourage $D_{n+1}\subseteq D_n$, followed by $\pl P$ choosing a point $p_{n+1}\in D_n[p_n]$.
    \end{itemize}
  At the conclusion of the game, $\pl D$ wins if either $\bigcap_{n<\omega}D_n[p_n]=\emptyset$ or $\<p_0,p_1,\dots\>$ converges, and $\pl P$ wins otherwise.
\end{defn}

The reader familiar with proximal spaces may note that this definition is different than the original formulation of the game (see \cite{b}); however, it is easily verified that $\pl D$ has a winning strategy in the original game if and only if $\pl D$ has a winning strategy in our version.   Also, if we wish we may assume that if $\sigma$ is a winning strategy for $\pl D$, then $D_{n+1}=\sigma (x_0,x_1,...,x_n)$ is contained in something smaller than $D_n$, e.g., $\frac{1}{4}D_n$.  That is because a sequence of legal moves by $\pl P$ with $\pl D$ using the refined strategy is also a legal sequence of moves with $\pl D$ using the original strategy.

\begin{defn}
  If a player $\pl P$ has a winning strategy in a game $G$, we write $\pl P\win G$. Otherwise, we write $\pl P\not\win G$.
\end{defn}

@@

\begin{defn}
  A space is said to be \term{Corson compact} if and only if it is homeomorphic to a compact set within the $\Sigma$-product $\Sigma\mathbb{R}^\kappa$ of $\kappa$-many real lines, that is:
    \[
      \Sigma\mathbb{R}^\kappa
        =
      \{x\in \mathbb{R}^\kappa: |\{\alpha:x(\alpha)\not=0\}|<\omega\}
    \]
\end{defn}

@@

\begin{proof}
  Let $\sigma$ be a winning strategy for $\pl D$ in the absolutely proximal game such that $p\supsetneq q$ implies $\sigma(p)\subset \frac{1}{4}\sigma(q)$.
  For any sequence $t=\<t_0,t_1,\dots\>$, let $o(t)$ be the subsequence of $t$ consisting of its odd-indexed terms.

  For certain finite sequences $s$ in $X$, we will define by induction a tree $T(s)$ of finite height such that $t\supset s$ implies $T(s)$ is a subtree of $T(t)$, and if $u$ is a node of $T(s)$ having successors in $T(s)$, then $u$ has no new successors in $T(t)$.   We let $\max(T)$ denote the nodes of $T$ that have no successors in $T$.

@@

First we define $T(\emptyset)$.

  \begin{itemize}
    \item Let $\emptyset\in T(\emptyset)$.
    \item Choose $m_\emptyset<\omega$, $h_{\emptyset,i}\in H$ for $i<m_\emptyset$, and $h_{\emptyset,i,j}\in H\cap\cl{\frac{1}{4}\sigma(\emptyset)[h_{\emptyset,i}]}$ for $i,j<m_\emptyset$ such that
      \[
        \left\{\frac{1}{4}\sigma(\emptyset)[h_{\emptyset,i}]:i<m_\emptyset\right\}
      \]
    is a cover for $H$ and such that for each $i<m_\emptyset$
      \[
        \left\{\frac{1}{4}\sigma(\<h_{\emptyset,i}\>)[h_{\emptyset,i,j}]:j<m_\emptyset\right\}
      \]
    is a cover for $H\cap\cl{\frac{1}{4}\sigma(\emptyset)[h_{\emptyset,i}]}$.
    \item Let $\<i\>, \<i,h_{\emptyset,i}\>$, and $\<i,h_{\emptyset,i},j\>$ be in $T(\emptyset)$ for $i,j<m_\emptyset$.
  \end{itemize}
This ends the construction of $T(\emptyset)$.   We remark that the indexings $i\mapsto h_{\emptyset,i}$ and $\<i,j\>\mapsto h_{\emptyset,i, j}$ need not be one-to-one; repetition of points is allowed.

@@

  Now suppose $T(a)$ is defined. We then define $T(a\concat\<x\>)$, etc., for
    \[
      x\in \bigcup_{s\concat\<i,h_{s,i},j\>\in\max(T(a))} \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]
    \]
  as follows:

  \begin{itemize}
    \item Let $T(a)\subseteq T(a\concat\<x\>)$.
    \item Choose $t=s\concat\<i,h_{s,i},j,x\>$ such that $s\concat\<i,h_{s,i},j\>\in\max(T(a))$ and $x\in \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]$.  Then $s\concat\<i,h_{s,i},j\>$ is the only node of $T(a)$ that will be extended in this step.
    \item Note that, assuming $o(s)\concat\<h_{s,i}\>$ is a legal partial attack against $\sigma$, then
      \[
        x
          \in
        \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]
          \subseteq
        \frac{1}{4}\sigma(o(s))[h_{s,i,j}]
      \]
    and
      \[
        h_{s,i,j}
          \in
        \cl{\frac{1}{4}\sigma(o(s))[h_{s,i}]}
          \subseteq
        \frac{1}{2}\sigma(o(s))[h_{s,i}]
      \]
    implies
      \[
        x
          \in
        \sigma(o(s))[h_{s,i}]
      \]
    and thus $o(s)\concat\<h_{s,i},x\>=o(t)$ is a legal partial attack against $\sigma$.
    \item Choose $m_t<\omega$, $h_{t,k}\in H\cap \cl{\frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]}$ for $k<m_t$, and $h_{t,k,l}\in H\cap\cl{\frac{1}{4}\sigma(o(t))[h_{t,k}]}$ for $k,l<m_t$ such that
      \[
        \left\{\frac{1}{4}\sigma(o(t))[h_{t,k}]:k<m_t\right\}
      \]
    is a cover for $H\cap \cl{\frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]}$ and such that for each $k<m_t$
      \[
        \left\{\frac{1}{4}\sigma(o(t)\concat\<h_{t,k}\>)[h_{t,k,l}]:l<m_t\right\}
      \]
    is a cover for $H\cap\cl{\frac{1}{4}\sigma(o(t))[h_{t,k}]}$.
    \item Note that, assuming $o(t)$ is a legal partial attack against $\sigma$, then
      \[
        h_{t,k}
          \in
        \cl{\frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]}
          \subseteq
        \frac{1}{2}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]
      \]
    and
      \[
        x
          \in
        \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]
      \]
    implies
      \[
        h_{t,k}
          \in
        \sigma(o(s)\concat\<h_{s,i}\>)[x]
      \]
    and thus $o(t)\concat\<h_{t,k}\>$ is a legal partial attack against $\sigma$.
    \item For each $k,l<m_t$, put $t\concat\<k,h_{t,k},l\>$ and all of its initial segments in $ T(a\concat\<x\>)$.   This completes the construction of  $ T(a\concat\<x\>)$.

@@

    \item Note that assuming
      \[
        \left\{\frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}] : s\concat\<i,h_{s,i},j\>\in\max(T(a))\right\}
      \]
    covers $H$, then since
      \[
        \left\{\frac{1}{4}\sigma(o(t)\concat\<h_{t,k}\>)[h_{t,k,l}] : s\concat\<i,h_{s,i},j,x,k,h_{t,k},l\>\in\max(T(a\concat\<x\>))\setminus\max(T(a))\right\}
      \]
    covers $H\cap \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]$, we have that
      \[
        \left\{\frac{1}{4}\sigma(o(t)\concat\<h_{t,k}\>)[h_{t,k,l}] : t\concat\<k,h_{t,k},l\>\in\max(T(a\concat\<x\>))\right\}
      \]
    covers $H$.
  \end{itemize}

@@

  If $p$ attacks $\tau$, then it follows that $T(p\rest n)$ is defined for all $n<\omega$, so let $T(p)=\bigcup_{n<\omega} T(p\rest n)$. We note $T(p)$ is an infinite tree with finite levels:
    \begin{itemize}
      \item $\emptyset$ has exactly $m_\emptyset$ successors $\<i\>$.
      \item $s\concat\<i\>$ has exactly one successor $s\concat\<i,h_{s,i}\>$
      \item $s\concat\<i,h_{s,i}\>$ has exactly $m_s$ successors $s\concat\<i,h_{s,i},j\>$
      \item $s\concat\<i,h_{s,i},j\>$ has either no successors or exactly one successor $s\concat\<i,h_{s,i},j,x\>$
      \item $t=s\concat\<i,h_{s,i},j,x\>$ has exactly $m_t$ successors $t\concat\<k\>$
    \end{itemize}

  Hence $T(p)$ has an infinite branch $q'=\<i_0,h_0,j_0,x_0,i_1,h_1,j_1,x_1,\dots\>$.   Let $q=o(q')=\<h_0,x_0,h_1,x_1,\dots\>$. Note that by the construction of $T(p)$, $q$ is an attack on the winning strategy $\sigma$ in the absolutely proximal game, so it must converge. Since every other term of $q$ is in $H$, it must converge to $H$. Then since $o(q)$ is a subsequence of $p$, $p$ must cluster at $H$.

  Since $\pl O\win\clusgame{X}{H}$ if and only if $\pl O\win\congame{X}{H}$, the result follows.
\end{proof}

>>>>

We quickly note two properites of $\frac{1}{2}D$.

\begin{prop}
  If $x\in \frac{1}{2}D[y]$ and $y\in \frac{1}{2}D[z]$, then $x\in D[z]$.
\end{prop}

@@

The theory of proximal uniform spaces relies on the following $\omega$-length 
game introduced in \cite{b}:

\begin{defn}
  The \textbf{proximal game} $\proxgame{X}$ of length $\omega$ played on a uniform space $X$ with two players $\pl D$, $\pl P$ proceeds as follows:
    \begin{itemize}
      \item In the initial round $0$, $\pl D$ chooses an open symmetric entourage $D_0$, followed by $\pl P$ choosing a point $p_0\in X$.
      \item In round $n+1$, $\pl D$ chooses an open symmetric entourage $D_{n+1}\subseteq D_n$, followed by $\pl P$ choosing a point $p_{n+1}\in D_n[p_n]$.
    \end{itemize}
  At the conclusion of the game, $\pl D$ wins if either $\bigcap_{n<\omega}D_n[p_n]=\emptyset$ or $\<p_0,p_1,\dots\>$ converges, and $\pl P$ wins otherwise.
  \footnote{It's worth noting that a widely distributed preprint of Bell's 
  paper considered $4D_n$ in place of $D_n$ for the winning
  condition; however, it's easily verified that player $\pl D$
  has a winning strategy in one if and only if she has a winning strategy in
  the other.}
\end{defn}

We may assume that if $\sigma$ is a winning strategy for $\pl D$, then $D_{n+1}=\sigma (x_0,x_1,...,x_n)$ is contained in something smaller than $D_n$, e.g., $\frac{1}{4}D_n$.  That is because a sequence of legal moves by $\pl P$ with $\pl D$ using the refined strategy is also a legal sequence of moves with $\pl D$ using the original strategy.

\begin{defn}
  If a player $\pl A$ has a winning strategy in a game $G$, we write $\pl A\win G$. Otherwise, we write $\pl A\not\win G$.
\end{defn}

@@

\begin{defn}
  A space is said to be \term{Corson compact} if and only if it is homeomorphic to a compact set within the $\Sigma$-product $\Sigma\mathbb{R}^\kappa$ of $\kappa$-many real lines, that is:
    \[
      \Sigma\mathbb{R}^\kappa
        =
      \{x\in \mathbb{R}^\kappa: |\{\alpha:x(\alpha)\not=0\}|\leq\omega\}
    \]
\end{defn}

@@

\begin{proof}
  Let $\sigma$ be a winning strategy for $\pl D$ in the absolutely proximal 
  game such that $p\supsetneq q$ implies $\sigma(p)\subseteq \frac{1}{4}\sigma(q)$.
  For any sequence $t=\<t_0,t_1,\dots\>$, let $o(t)=\<t_1,t_3,\dots\>$ 
  be the subsequence of $t$ 
  consisting of its odd-indexed terms. We proceed by constructing a winning
  strategy for $\pl O$ in $\clusgame{X}{H}$. Since $\pl O\win\clusgame{X}{H}$ 
  if and only if $\pl O\win\congame{X}{H}$, the result will follow.

@@

First we define a tree $T(\emptyset)$. Our aim is to define an open set
  \[
    \bigcup_{i,j<m_\emptyset}
      \frac{1}{4}\sigma(\<h_{\emptyset,i}\>)[h_{\emptyset,i,j}]
    =
    \bigcup_{\<i,h_{\emptyset,i},j\>\in\max(T(\emptyset))} 
      \frac{1}{4}\sigma(o(\emptyset)\concat\<h_{\emptyset,i}\>)[h_{\emptyset,i,j}]
  \]
which contains $H$, and $\pl O$ will use this as the inital move in her winning 
strategy for $\clusgame{X}{H}$.

  \begin{itemize}
    \item Choose $m_\emptyset<\omega$, $h_{\emptyset,i}\in H$ for $i<m_\emptyset$, and $h_{\emptyset,i,j}\in H\cap\cl{\frac{1}{4}\sigma(\emptyset)[h_{\emptyset,i}]}$ for $i,j<m_\emptyset$ such that
      \[
        \left\{\frac{1}{4}\sigma(\emptyset)[h_{\emptyset,i}]:i<m_\emptyset\right\}
      \]
    is a cover for $H$ and such that for each $i<m_\emptyset$
      \[
        \left\{\frac{1}{4}\sigma(\<h_{\emptyset,i}\>)[h_{\emptyset,i,j}]:j<m_\emptyset\right\}
      \]
    is a cover for $H\cap\cl{\frac{1}{4}\sigma(\emptyset)[h_{\emptyset,i}]}$.

    (The indexings $i\mapsto h_{\emptyset,i}$ and 
    $\<i,j\>\mapsto h_{\emptyset,i, j}$ need not be 
    one-to-one; repetition of points is allowed.)
    \item Let $\<i,h_{\emptyset,i},j\>$ and its initial segments be in 
    $T(\emptyset)$ for $i,j<m_\emptyset$.
  \end{itemize}

@@

Now suppose that $a$ is a finite 
sequence of moves by $\pl P$ in $\clusgame{X}{H}$ for which $\pl O$ replied with
  \[
    \bigcup_{s\concat\<i,h_{s,i},j\>\in\max(T(a))} 
      \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]
  \]
as a part of her winning strategy for some tree $T(a)\supseteq T(\emptyset)$. 
As we will soon guarantee, any nonempty $s$ will be of the form 
$\<i_0,h_0,j_0,x_0,\dots\>$ so that 
$o(s)\concat\<h_{s,i}\> = \<h_0,x_0,\dots,h_{s,i}\>\in X^{<\omega}$ 
corresponds to a partial attack against $\sigma$ by the proximal game's $\pl P$. 
We then define $T(a\concat\<x\>)$ for each of the legal responses
  \[
    x\in 
      \bigcup_{s\concat\<i,h_{s,i},j\>\in\max(T(a))} 
      \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]
  \]
by the clustering game's $\pl P$ as follows:

  \begin{itemize}
    \item Fix $s\concat\<i,h_{s,i},j\>\in\max(T(a))$ such that 
      $x\in \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]$.  
      Then $s\concat\<i,h_{s,i},j\>$ is the only node of $T(a)$ that will be 
      extended in this step. Let $t=s\concat\<i,h_{s,i},j,x\>$.
    \item Note that, assuming $o(s)\concat\<h_{s,i}\>$ is a legal partial attack against $\sigma$, then
      \[
        x
          \in
        \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]
          \subseteq
        \frac{1}{4}\sigma(o(s))[h_{s,i,j}]
      \]
    and
      \[
        h_{s,i,j}
          \in
        \cl{\frac{1}{4}\sigma(o(s))[h_{s,i}]}
          \subseteq
        \frac{1}{2}\sigma(o(s))[h_{s,i}]
      \]
    implies
      \[
        x
          \in
        \sigma(o(s))[h_{s,i}]
      \]
    and thus $o(s)\concat\<h_{s,i},x\>=o(t)$ is a legal partial attack against $\sigma$.
    \item Choose $m_t<\omega$, $h_{t,k}\in H\cap \cl{\frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]}$ for $k<m_t$, and $h_{t,k,l}\in H\cap\cl{\frac{1}{4}\sigma(o(t))[h_{t,k}]}$ for $k,l<m_t$ such that
      \[
        \left\{\frac{1}{4}\sigma(o(t))[h_{t,k}]:k<m_t\right\}
      \]
    is a cover for $H\cap \cl{\frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]}$ and such that for each $k<m_t$
      \[
        \left\{\frac{1}{4}\sigma(o(t)\concat\<h_{t,k}\>)[h_{t,k,l}]:l<m_t\right\}
      \]
    is a cover for $H\cap\cl{\frac{1}{4}\sigma(o(t))[h_{t,k}]}$.
    \item Note that, assuming $o(t)$ is a legal partial attack against $\sigma$, then
      \[
        h_{t,k}
          \in
        \cl{\frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]}
          \subseteq
        \frac{1}{2}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]
      \]
    and
      \[
        x
          \in
        \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]
      \]
    implies
      \[
        h_{t,k}
          \in
        \sigma(o(s)\concat\<h_{s,i}\>)[x]
      \]
    and thus $o(t)\concat\<h_{t,k}\>$ is a legal partial attack against $\sigma$.

    \item Let $T(a\concat\<x\>)\supseteq T(a)$, and for each $k,l<m_t$, 
    also let $t\concat\<k,h_{t,k},l\>$ and all of its initial segments be in 
    $T(a\concat\<x\>)$.
  \end{itemize}

@@

 This completes the construction of  $ T(a\concat\<x\>)$. Note that assuming
    \[
      \left\{\frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}] : s\concat\<i,h_{s,i},j\>\in\max(T(a))\right\}
    \]
  covers $H$, then since
    \[
      \left\{\frac{1}{4}\sigma(o(t)\concat\<h_{t,k}\>)[h_{t,k,l}] : s\concat\<i,h_{s,i},j,x,k,h_{t,k},l\>\in\max(T(a\concat\<x\>))\setminus\max(T(a))\right\}
    \]
  covers $H\cap \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]$, we have that
    \[
      \left\{\frac{1}{4}\sigma(o(t)\concat\<h_{t,k}\>)[h_{t,k,l}] : t\concat\<k,h_{t,k},l\>\in\max(T(a\concat\<x\>))\right\}
    \]
  covers $H$.

@@

  If $p$ is an attack by $\pl P$ against $\tau$, then it follows that $T(p\rest n)$ is defined for all $n<\omega$, so let $T(p)=\bigcup_{n<\omega} T(p\rest n)$. We note $T(p)$ is an infinite tree with finite levels:
    \begin{itemize}
      \item $\emptyset$ has exactly $m_\emptyset$ successors $\<i\>$.
      \item $s\concat\<i\>$ has exactly one successor $s\concat\<i,h_{s,i}\>$
      \item $s\concat\<i,h_{s,i}\>$ has exactly $m_s$ successors $s\concat\<i,h_{s,i},j\>$
      \item $s\concat\<i,h_{s,i},j\>$ has either no successors or exactly one successor $s\concat\<i,h_{s,i},j,x\>$
      \item $t=s\concat\<i,h_{s,i},j,x\>$ has exactly $m_t$ successors $t\concat\<k\>$
    \end{itemize}

  Hence $T(p)$ has an infinite branch $q'=\<i_0,h_0,j_0,x_0,i_1,h_1,j_1,x_1,\dots\>$.   Let $q=o(q')=\<h_0,x_0,h_1,x_1,\dots\>$. Note that by the construction of $T(p)$, $q$ is an attack on the winning strategy $\sigma$ in the absolutely proximal game, so it must converge. Since every other term of $q$ is in $H$, it must converge to $H$. Then since $o(q)$ is a subsequence of $p$, $p$ must cluster at $H$.
\end{proof}
